\label{sec:credits}
\begin{thebibliography}{References}
\bibitem{C-WindowsInstaller}The ImageJ installer for Windows is created
using the \href{http://www.jrsoftware.org/isinfo.php}{Inno Setup}
installer generator. \filenameref{ImageJ.exe} the Windows that launches
ImageJ (\filenameref{ij.jar}) was contributed by George Silva.

\bibitem{C-ZIPcompressedTIFFs}Support for ZIP-compressed TIFFs was
contributed by Jason Newton in IJ\,1.45g.

\bibitem{C-FxFinder}The macro editor's Function Finder (\textsf{\userinterface{\textsf{Macros\lyxarrow{}Find Functions...}}})
was written by Jérôme Mutterer.

\bibitem{C-EllipseTool}The \nameref{sub:Elliptical-Selection-Tool}
was contributed by Norbert Vischer.

\bibitem{C-ROIbrush}The \nameref{sub:Brush-Selection-Tool} is based
on the \href{http://imagej.nih.gov/ij/plugins/roi-brush.html}{ROI Brush Tool}
plugin from Tom Larkworthy and Johannes Schindelin.

\bibitem{C-ArrowTool}Jean-Yves Tinevez and Johannes Schindelin (authors
of the \href{http://fiji.sc/wiki/index.php/Arrow}{Fiji Arrow Tool})
contributed code to the \nameref{sec:Arrow-Tool}.

\bibitem{C-WandTool}Michael Schmid, added 4--connected and 8--connected
tracing with tolerance to the \nameref{sub:Wand-Tool}.

\bibitem{C-Toolsets}Macro Toolsets distributed with ImageJ have been
contributed by Gilles Carpentier, Jérôme Mutterer and Tiago Ferreira.

\bibitem{C-PixelInspector}The \nameref{sub:PixelInspector} is a
plugin tool conversion of Michael Schmid's \href{http://imagejdocu.tudor.lu/doku.php?id=plugin:utilities:pixel_inspector:start}{Pixel Inspector}
plugin.

\bibitem{C-ImportResults}In IJ\,1.43l and earlier, the \textsf{\userinterface{\textsf{File\lyxarrow{}Import\lyxarrow{}}\nameref{sub:Import>Results}}}
command was based on Jérôme Mutterer's \href{http://imagej.nih.gov/ij/macros/Import_Results_Table.txt}{Import\_{}Results\_{}Table}
macro.

\bibitem{C-StackFromList}Marcel van Herk added URLs support to the
\textsf{\userinterface{\textsf{File\lyxarrow{}Import\lyxarrow{}}\nameref{sub:Stack-From-List...}}
}command in IJ\,1.45f.

\bibitem{C-AviPlugins}Michael Schmid contributed improvements to
the \href{http://imagej.nih.gov/ij/source/ij/plugin/AVI_Reader.java}{AVI reader}
and \href{http://imagej.nih.gov/ij/source/ij/plugin/filter/AVI_Writer.java}{AVI writer}
plugins.

\bibitem{C-FITSwriter}Karen Collins contributed improvements to the
FITS\_Writer (\textsf{\userinterface{\textsf{File\lyxarrow{}Save As\lyxarrow{}}\nameref{sub:FITS...}}}
command).

\bibitem{C-FitCircle}The \textsf{\userinterface{\textsf{Edit\lyxarrow{}Selection\lyxarrow{}}\nameref{sub:Fit-Circle}}}
command, based on a MATLAB script by \href{http://www.math.uab.edu/~chernov/cl/MATLABcircle.html}{Nikolai Chernov},
was contributed by Michael Doube and Ved Sharma.

\bibitem{C-CreateSelection}The \userinterface{\textsf{Edit\lyxarrow{}Selection\lyxarrow{}}\nameref{sub:Create-Selection}}
command is based on the Threshold\_To\_Selection plugin written by
Johannes Schindelin.

\bibitem{C-SocketListener}IJ\,1.46f adopted Johannes Schindelin's
RMI-based \href{http://fiji.sc/javadoc/fiji/OtherInstance.html}{OtherInstance}
class from Fiji, which works on multi-user machines and is more secure.

\bibitem{C-CP}The Color Picker (\userinterface{\textsf{Image\lyxarrow{}Color\lyxarrow{}}\nameref{sub:Color-Picker...[K]}})
was written by Gali Baler, a 2003--2004 intern from \href{http://www.montgomeryschoolsmd.org/schools/bcchs/}{Bethesda-Chevy Chase High School}.

\bibitem{C-ThresMeth}The 16\,different thresholding methods available
in the \textsf{\userinterface{\textsf{Image\lyxarrow{}Adjust\lyxarrow{}\nameref{sub:Threshold...[T]}}}}
tool were implemented by Gabriel Landini.

\bibitem{C-Resizer-Scaler}Michael Schmid contributed improvements
to the downsizing kernel used by \textsf{\userinterface{\textsf{Image\lyxarrow{}Adjust\lyxarrow{}}\nameref{sub:Size...}}}
and \textsf{\userinterface{\textsf{Image\lyxarrow{}}\nameref{sub:Scale...[E]}}}
as well as undo support for \textsf{\userinterface{\textsf{Image\lyxarrow{}}\nameref{sub:Scale...[E]}}}.

\bibitem{C-ColorThres}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Adjust\lyxarrow{}}\nameref{sub:Color-Threshold...}}}
command implements Gabriel Landini's \href{http://www.dentistry.bham.ac.uk/landinig/software/software.html}{Threshold Colour plugin}.

\bibitem{C-Reslice-Zproj}The \href{http://imagej.nih.gov/ij/source/ij/plugin/Slicer.java}{Reslice}
and the \href{http://imagej.nih.gov/ij/source/ij/plugin/ZProjector.java}{ZProject}
plugin (\textsf{\userinterface{\textsf{Image\lyxarrow{}Stacks\lyxarrow{}}\nameref{sub:Reslice...[/]}}}
and \userinterface{\nameref{sub:Z-Project...}} commands) were contributed
by Patrick Kelly and Harvey Karten of the University of California,
San Diego.

\bibitem{C-OrthoViews}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Stacks\lyxarrow{}}\nameref{sub:Orthogonal-Views}}}
command is based on Dimiter Prodanov's \href{http://imagej.nih.gov/ij/plugins/stack-slicer/index.html}{StackSlicer}
plugin and Albert Cardona's Updater class. Michael Doube added support
for XZ and YZ view control as well as mouse wheel control.

\bibitem{C-3Dproject-1}The\textsf{ \userinterface{\textsf{Image\lyxarrow{}Stacks\lyxarrow{}}\nameref{sub:3D-Project...}}}
was written by Michael Castle and Janice Keller of the University
of Michigan Mental Health Research Institute (MHRI). Bill Mohler added
suport for hyperstacks and 16/32--bit images in IJ\,1.44m.

\bibitem{C-Concatenator}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Stacks\lyxarrow{}Tools\lyxarrow{}}\nameref{sub:Concatenate...}}}
command implemented in IJ\,1.46e is based on the \href{http://imagej.nih.gov/ij/plugins/concatenate.html}{Concatenate}
plugin by Jonathan Jackson.

\bibitem{C-SubstackMaker}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Stacks\lyxarrow{}Tools\lyxarrow{}}\nameref{par:Make-Substack}}}
command is based on the \href{http://imagej.nih.gov/ij/plugins/substack-maker.html}{Substack Maker}
plugin by Anthony Padua, Daniel Barboriak and Ved Sharma.

\bibitem{C-ReduceDimens}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Hyperstacks\lyxarrow{}}\nameref{sub:Reduce-Dimensionality...}}}
command is based Jérôme Mutterer's \href{http://imagej.nih.gov/ij/macros/Reduce_HyperStack.txt}{Reduce HyperStack}
macro.

\bibitem{C-Binner}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Transform\lyxarrow{}}\nameref{sub:Bin...}}}
command is based on Nico Stuurman's \href{http://valelab.ucsf.edu/~nico/IJplugins/Binner.html}{Binner}
plugin.

\bibitem{C-SetZoom}The \textsf{\userinterface{\textsf{Image\lyxarrow{}Zoom\lyxarrow{}}\nameref{sub:Set-Zoom...}}}\textsf{\small{}
}command is based on Albert Cardona's \href{http://albert.rierol.net/software.html}{Zoom Exact}
plugin.

\bibitem{C-Find-Maxima}The \textsf{\userinterface{\textsf{Process\lyxarrow{}}\nameref{sub:Find-Maxima}}}
command is based on a plugin contributed by Michael Schmid.

\bibitem{C-EnhContrast}The equalization code implemented in \textsf{\userinterface{\textsf{Process\lyxarrow{}}\nameref{sub:Enhance-Contrast}}}
was contributed by Richard Kirk.

\bibitem{C-RemoveNaNs}The \textsf{\userinterface{\textsf{Process\lyxarrow{}}Noise\textsf{\lyxarrow{}}\nameref{sub:Remove-NaNs...}}}was
contributed by Michael Schmid.

\bibitem{C-MathMacro}The \textsf{\userinterface{\textsf{Process\lyxarrow{}Math\lyxarrow{}}\nameref{sub:Macro...}}}
command is modeled after Ulf Dittmer's \href{http://www.ulfdittmer.com/imagej/index.html\#Expression}{Expression}
plugin.

\bibitem{C-FFTfilter}The \textsf{\userinterface{\textsf{Process\lyxarrow{}FFT\lyxarrow{}}\nameref{sub:Bandpass-Filter...}}}
is a built in version of Joachim Walter's \href{http://imagej.nih.gov/ij/plugins/fft-filter.html}{FFT Filter}
plugin.

\bibitem{C-Fill-Holes}The \textsf{\userinterface{\textsf{Process\lyxarrow{}Binary\lyxarrow{}}\nameref{sub:Fill-Holes}}}
algorithm was contributed by Gabriel Landini.

\bibitem{C-Skeletonize3D}The \href{http://fiji.sc/wiki/index.php/Skeletonize3D}{Skeletonize3D}
plugin was written by Ignacio Arganda-Carreras, based on an \nomenclature{ITK}{Insight Segmentation and Registration}\href{http://itk.org/itkindex.html}{ITK}
implementation by \href{http://hdl.handle.net/1926/1292}{Hanno Homann}.
It implements a 3D thinning algorithm from Lee et al.\ \href{http://dx.doi.org/10.1006/cgip.1994.1042}{Building skeleton models via 3-D medial surface axis thinning algorithms}.\ \emph{CVGIP},
56(6):462--478, 1994. 

\bibitem{C-MultiThreadFilters}Multi-threading support for all \textsf{\userinterface{\textsf{Process\lyxarrow{}}\nameref{sub:Filters}}}
commands was contributed by Stephan Saalfeld and Michael Schmid in
ImageJ\,1.45c.

\bibitem{C-GaussianBlur}The faster and more accurate version of\textsf{
\userinterface{\textsf{Process\lyxarrow{}Filters\lyxarrow{}}\nameref{sub:Gaussian-Blur...}}}
implemented in ImageJ\,1.38r was contributed by Michael Schmid.

\bibitem{C-NonBlockingDialog}The \texttt{\code{\texttt{NonBlockingGenericDialog.class}}}
used by the \userinterface{\textsf{Process\lyxarrow{}Batch\lyxarrow{}}\nameref{sub:batch>Macro...}}
command was added by Johannes Schindelin.

\bibitem{C-SubtractBackground}The rolling ball code of \textsf{\userinterface{\textsf{Process\lyxarrow{}}\nameref{sub:Subtract-Background...}}}
is based on the NIH Image Pascal version by Michael Castle and Janice
Keller. The sliding paraboloid algorithm was written by Michael Schmid.

\bibitem{C-Distribution}The \textsf{\userinterface{\textsf{Analyze\lyxarrow{}}\nameref{sub:Distribution...}}}
command was written by Gabriel Landini.

\bibitem{C-Histogram}The scaled color bar implemented in \textsf{\userinterface{\textsf{Analyze\lyxarrow{}}\nameref{sub:Histogram}}}
was contributed by Bob Dougherty. 

\bibitem{C-CurveFitter}The much improved \href{http://imagej.nih.gov/ij/developer/api/ij/measure/CurveFitter.html}{CurveFitter}
(\textsf{\userinterface{\textsf{Analyze\lyxarrow{}Tools\lyxarrow{}}\nameref{sub:Curve-Fitting...}}})
implemented in IJ\,1.46f was contributed by Michael Schmid. The Rodboard
and Gaussian functions were originally contributed by David Rodbard
(NIH) and Stefan W\"orz (DKFZ), respectively.

\bibitem{C-RM-XOR}The ROI\ Manager(\emph{XOR}) command (\textsf{\userinterface{\textsf{Analyze\lyxarrow{}Tools\lyxarrow{}}\nameref{sub:ROI-Manager...}}})
was added by Johannes Schindelin.

\bibitem{C-RM-MultiMeasure}The ROI\ Manager(\emph{Multi\ Measure})
command (\textsf{\userinterface{\textsf{Analyze\lyxarrow{}Tools\lyxarrow{}}\nameref{sub:ROI-Manager...}}})
is based on Bob Dougherty's Multi\_Measure plugin.

\bibitem{C-RM-MultiPlot}The ROI\ Manager(\emph{Multi\ Plot}) command
(\textsf{\userinterface{\textsf{Analyze\lyxarrow{}Tools\lyxarrow{}}\nameref{sub:ROI-Manager...}}})
was contributed by Philippe Gendre.

\bibitem{C-SyncWIndows}The \userinterface{Analyze\lyxarrow{}Tools\lyxarrow{}\nameref{sub:SynchronizeWindows}}
command (an improved version of the \href{http://imagej.nih.gov/ij/plugins/ucsd.html}{SyncWindows\_{} plugin}
by Patrick Kelly) was contributed by Joachim Walter.

\bibitem{C-ControlPanel}The Control Panel (\textsf{\userinterface{\textsf{Plugins\lyxarrow{}Utilities\lyxarrow{}}\nameref{sub:Control-Panel...}}})
was written by Cezar M.\ Tigare.

\bibitem{C-ComandFinder}The Command Finder (\textsf{\userinterface{\textsf{Plugins\lyxarrow{}Utilities\lyxarrow{}}\nameref{sub:Command-Finder}}})
was written by Mark Longair.

\bibitem{C-PluginTool}The \filenameref{\href{http://imagej.nih.gov/ij/source/ij/plugin/tool/PlugInTool.java}{PlugInTool}}
class was inspired by Johannes Schindelin's \href{http://fiji.sc/javadoc/fiji/tool/AbstractTool.html}{AbstractTool}
class in Fiji.

\bibitem{C-Several}Other additions, improvements and reproducible
 bug reports have been contributed by Adrian Daerr, Airen Peraza,
Ajay Gopal, Albert Cardona, Alberto Duina, Alden Dima, Andreas Maier,
Andrew French, Andrii Savchenko, Arttu Miettinen, Aryeh Weiss, Balazs
Nyiri, Barry DeZonia, Bill Mohler, Bob Hamilton, Bob Loushin, Bruno
Vellutini, Burri Olivier, Carlos Becker, Carne Draug, Charles Anderson,
Cheryl McCreary, Christian Moll, Christophe Leterrier, Christopher
Harrison, Damon Poburko, Daniel Hornung, Daniel Kalthoff, Daniel Senff,
David Gauntt, David McDonald, Denny Hugg, Dimiter Prodanov, Divakar
Ramachandran, Dorai Iyer, Duncan Mak, Eik Schumann, Emmanuel Levy,
Erik Meijering, Fabian Svara, Francis Burton, Frank Sprenger, Franklin
Shaffer, Frederic Hessman, Gabriel Landini, Gilles Carpentier, Gregory
Reneff, Hiroki Hakoshima, Ian Lim, Ingo Bartholomaeus, Jakob Preus,
Jamie Robinson, Jan Eglinger, Jan Funke, Jarek Sacha, Jay Unruh, Jean-Pierre
Clamme, Jerome Mutterer, Jesper Pedersen, Jim Passmore, Joachim Wesner,
Johannes Hermen, Johannes Schindelin, Johannes Weissmann, John Oreopoulos,
John Pearl, Jonathan Silver, Jose Wojnacki, Juan Grande, Julian Cooper,
Kai Uwe Barthel, Karen Collins, Kees Straatman, Kevin Moll, Kris Sheets,
Mark Krebs, Mark Longair, Martin Dressler, Mat Al-Tamimi, Matthew
Smith, Michael Cammer, Michael Doube, Michael Ellis, Michael Schmid,
Michel Julier, Nagananda Gurudev, Nico Stuurman, Norbert Vischer,
Olaf Freyer, Oliver Bannach, Olivier Bardot, Paul Jurczak, Peter Haub,
Rainer Engel, Raymond Coory, Reinhard Mayr, Richard Cole, Richie Mort,
Robert Dougherty, Shannon Stewman, Simon Roussel, Stefan Starke, Stephan
Saalfeld, Steven Green, Thomas Boudier, Thorsten Wagner, Tiago Ferreira,
Tomas Karlsson, Tseng Qingzong, Ulf Dittmer, Uwe Walschus, Valerio
Mussi, Ved Sharma, Vytas Bindokas, Wilhelm Burger, Winfried Wurm,
Xiao Chen, Zeljka Maglica.

\end{thebibliography}
\vspace*{60pt}

\begin{infobox}
\caption{\label{infobox:focus}Focus on Bioimage Informatics}


In July 2012 Nature Methods issued a \href{http://www.nature.com/nmeth/focus/bioimageinformatics/index.html}{focus}
dedicated to the role of bioimage informatics in microscopy, the tools
that are available for scientific image processing, and the challenges
and opportunities in the field. The special issue features a large
collection of articles discussing ImageJ, \nameref{sub:Fiji-intro}
and \nameref{sub:Related-Software}, including:
\begin{itemize}
\item {\small Cardona A, Tomancak P: ``Current challenges in open-source
bioimage informatics'' \cite{Cardona:2012p21002}}{\small \par}
\item {\small Carpenter AE et al.: ``A call for bioimaging software usability''
\cite{Carpenter:2012p21003}}{\small \par}
\item {\small Eliceiri KW. ``Biological imaging software tools'' \cite{Eliceiri:2012p21007}}{\small \par}
\item {\small Schindelin J et al. ``Fiji: an open-source platform for biological-image
analysis'' \cite{Schindelin:2012p21012}}{\small \par}
\item {\small Schneider CA et al.: ``NIH Image to ImageJ: 25 years of image
analysis'' \cite{Schneider:2012p20999}}{\small \par}
\end{itemize}
A full announcement can be found on the \href{http://fiji.sc/wiki/index.php/2012-06-29_-_Fiji_papers_at_Nature_Methods}{Fiji news channel}.
\end{infobox}

